Adaption of the Chumbley Score to matching of bullet striation marks

### 2017-10-20 doc/paper.Rmd
,,

\citep{chumbley} found that the algorithm gives false-positives in slightly over 2 cases (or 2%) of the time and about 9 false-negatives (or 9%) for every 100 comparisons. \citep{hadler} on the other hand, in the improved version of the algorithm first described by \citep{chumbley} found a false-positives for 0 cases and 3 false-negatives (or 6%) for 50 comparisons of knwon matches.
\begin{figure}
\centering
\includegraphics[width=\textwidth]{images/B6-B2-L6.png}
```{r, echo=FALSE, fig.width=8, fig.height=3, out.width='\\textwidth'}
land <- read.csv("../data/b6b2l6.csv")
land %>% ggplot(aes(x = y, y=resid)) +geom_line() +theme_bw()
```

@@

In case of

>>>>

\citep{chumbley} found that the algorithm gives false-positives in slightly over 2 cases (or 2%) of the time and about 9 false-negatives (or 9%) for every 100 comparisons. \citep{hadler} on the other hand, in the improved version of the algorithm first described by \citep{chumbley} found false-positives for 0 cases and 3 false-negatives (or 6%) for 50 comparisons of knwon matches.
\begin{figure}
\centering
\includegraphics[width=\textwidth]{images/B6-B2-L6.png}
```{r, echo=FALSE, fig.width=8, fig.height=3, out.width='\\textwidth'}
land <- read.csv("../data/b6b2l6.csv")
land %>% ggplot(aes(x = y, y=resid)) +geom_line() +theme_bw()
```

@@
